Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-05-26 props.tex
Slightly cleaner, factored out policy failure case

    An observational prefix \(O_1 \lesssim O_2\) means that \(O_1\) is a prefix of \(O_2\) up to the deletion
    of \(\tau\) observations:
    \[\begin{split}
      O_1 & \sim O_2 \triangleq \forall o . o \in O_1 \Rightarrow o = \tau \lor \\
      & \exists O_1' . O_1 = \tau O_1' \land O_1' \sim O_2 \lor \\
      & \exists O_2' .  O_2 = \tau O_2' \land O_1 \sim O_2' \lor \\
      & \exists O_1' O_2' . O_1 = w O_1' \land O_2 = w O_2' \land O_1' \sim O_2' \\
    \end{split}\]

    Observational equivalence is defined as traces prefixing each other:
    \[O_1 \simeq O_2 \triangleq O_1 \lesssim O_2 \land O_2 \lesssim O_1\]

@@

      \begin{itemize}
        \item Let \(m_0,\mathit{pinit}(m_0) \hookrightarrow \MP\) and \(m_0' \hookrightarrow M'\)
        \item If \(\MP \in \top\) then \(\mathit{Obs}(\MP) \simeq \mathit{Obs}(M')\)
        \item Otherwise \(\mathit{Obs}(\MP) \lesssim \mathit{Obs}(M')\)
      \end{itemize}

@@

          \begin{itemize}
            \item Let \(C = \mathit{Cof}(m_c,n)\)
            \item Let \(m_r' = \mathit{roll}_I(C,m_c,m_r)\), \((m_r,p_r) \hookrightarrow \MP\), and
              \(m_r' \hookrightarrow M'\)
            \item If \(m_r,p_r \hookrightarrow \MP \in \top\) then \(\mathit{Obs}(\MP) \simeq \mathit{Obs}(M')\)
            \item Otherwise \(\mathit{Obs}(\MP) \lesssim \mathit{Obs}(M')\)
          \end{itemize}

@@

      \begin{itemize}
        \item Let \(C = \mathit{Cof}(m_c,n)\)
        \item For all \(m_c'\) such that \(m_c \approx_C m_c'\):
        \item If \((m_c,p_c) \hookrightarrow \MP_1 (m_r,p_r) | \mathit{ret}\ m_r\ a_{pc}\ a_{sp}\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where
              \(m_c' \hookrightarrow M_1' m_r' | \mathit{ret}\ m_r'\ a_{pc}\ a_{sp}\)
            \item Let \(m_r'' = \mathit{roll}_C(C,m_c,m_r,m_c',m_r')\),
              \((m_r,p_r) \hookrightarrow \MP_2\), and \(m_r'' \hookrightarrow M_2'\)
            \item If \(\MP \in \top\) then \(\mathit{Obs}(\MP_1) \cdot \mathit{Obs}(\MP_2) \simeq
              \mathit{Obs}(M_1') \cdot \mathit{Obs}(M_2')\)
            \item Otherwise \(\mathit{Obs}(\MP_1) \cdot \mathit{Obs}(\MP_2) \lesssim
              \mathit{Obs}(M_1') \cdot \mathit{Obs}(M_2')\)
          \end{itemize}
        \item Else, for \(\MP\) and \(M'\) such that \(m_c,p_c \hookrightarrow \MP\) and \(m_c' \hookrightarrow M'\):
          \begin{itemize}
            \item If \(\MP \in \top\) then \(\mathit{Obs}(\MP) \simeq \mathit{Obs}(M')\)
            \item Otherwise \(\mathit{Obs}(\MP) \lesssim \mathit{Obs}(M')\)
          \end{itemize}
      \end{itemize}

@@

      \begin{itemize}
        \item Let \(C = \mathit{Cof}(m_c,n)\)
        \item For all \(m_c'\) such that \(m_c \approx_C m_c'\):
        \item If \((m_c,p_c) \hookrightarrow_P \MP (m_r,p_r) | \mathit{ret}\ m_r\ a_{pc}\ a_{sp}\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where
              \(m_c' \hookrightarrow M m_r' | \mathit{ret}\ m_c'\ m_r'\)
            \item \(\mathit{Obs}(\MP) \simeq \mathit{Obs}(M)\)
            \item And for all \(k\), if \(m_c(k) \not = m_r(k)\) or \(m_c'(k) \not = m_r'(k)\),
              \(m_r(k) = m_r'(k)\)
          \end{itemize}
        \item Else, for \(\MP\) and \(M'\) such that \(m_c,p_c \hookrightarrow \MP\) and \(m_c' \hookrightarrow M'\)
          \begin{itemize}
            \item If \(\MP \in \top\) then \(\mathit{Obs}(\MP) \simeq \mathit{Obs}(M')\)
            \item Otherwise \(\mathit{Obs}(\MP) \lesssim \mathit{Obs}(M')\)
          \end{itemize}
      \end{itemize}

>>>>

    An observational prefix \(O_1 \lesssim O_2\) means that \(O_1\) is a prefix of \(O_2\) up to the deletion
    of \(\tau\) observations:
    \[\begin{split}
      O_1 & \lesssim O_2 \triangleq \forall o . o \in O_1 \Rightarrow o = \tau \lor \\
      & \exists O_1' . O_1 = \tau O_1' \land O_1' \lesssim O_2 \lor \\
      & \exists O_2' .  O_2 = \tau O_2' \land O_1 \lesssim O_2' \lor \\
      & \exists O_1' O_2' . O_1 = w O_1' \land O_2 = w O_2' \land O_1' \lesssim O_2' \\
    \end{split}\]

    Equivalence of observation traces is defined as traces prefixing each other:
    \[O_1 \simeq O_2 \triangleq O_1 \lesssim O_2 \land O_2 \lesssim O_1\]

    We define policy-sensitive observational equivalence, which relates machine traces and
    {\it mptraces} whose observable behavior match up to a possible halt due to policy failure.
    It relates lists of parameters as long as only the last is infinite.

    \[\frac{\MP \not \in \top \hspace{.5cm} \mathit{Obs}(\MP) \lesssim \mathit{Obs}(M)}
           {\MP \sim_P M}\]

    \[\frac{\MP \in \top \hspace{.5cm} \mathit{Obs}(\MP) \simeq \mathit{Obs}(M)}
           {\MP \sim_P M}\]

    \[\frac{\begin{split}
              \MP \not \in \top & \hspace{.5cm} M \not \in \top \\
              \mathit{Obs}(\MP) \simeq \mathit{Obs}(M) & \hspace{.5cm} \overline{\MP} \sim_P \overline{M} \\
            \end{split}}
           {\MP \overline{\MP} \sim_P M \overline{M}}\]

@@

      \begin{itemize}
        \item Let \(m_0,\mathit{pinit}(m_0) \hookrightarrow \MP\) and \(m_0' \hookrightarrow M'\)
        \item \(\MP \sim M'\)
      \end{itemize}

@@

          \begin{itemize}
            \item Let \(C = \mathit{Cof}(m_c,n)\)
            \item Let \(m_r' = \mathit{roll}_I(C,m_c,m_r)\), \((m_r,p_r) \hookrightarrow \MP\), and
              \(m_r' \hookrightarrow M'\)
            \item \(\MP \sim_P M'\)
          \end{itemize}

@@

      \begin{itemize}
        \item Let \(C = \mathit{Cof}(m_c,n)\)
        \item For all \(m_c'\) such that \(m_c \approx_C m_c'\):
        \item If \((m_c,p_c) \hookrightarrow \MP_1 (m_r,p_r) | \mathit{ret}\ m_r\ a_{pc}\ a_{sp}\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where

              \(m_c' \hookrightarrow M_1' m_r' | \mathit{ret}\ m_r'\ a_{pc}\ a_{sp}\)
            \item Let \(m_r'' = \mathit{roll}_C(C,m_c,m_r,m_c',m_r')\),

              \((m_r,p_r) \hookrightarrow \MP_2\), and \(m_r'' \hookrightarrow M_2'\)
            \item \(\MP_1 \MP_2 \sim_P M_1' M_2'\)
          \end{itemize}
        \item Else, for \(\MP\) and \(M'\) such that \(m_c,p_c \hookrightarrow \MP\) and \(m_c' \hookrightarrow M'\),
          \(\MP \sim_P M'\)
      \end{itemize}

@@

      \begin{itemize}
        \item Let \(C = \mathit{Cof}(m_c,n)\)
        \item For all \(m_c'\) such that \(m_c \approx_C m_c'\):
        \item If \((m_c,p_c) \hookrightarrow_P \MP (m_r,p_r) | \mathit{ret}\ m_r\ a_{pc}\ a_{sp}\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where

              \(m_c' \hookrightarrow M m_r' | \mathit{ret}\ m_c'\ m_r'\)
            \item \(\mathit{Obs}(\MP) \simeq \mathit{Obs}(M)\)
            \item And for all \(k\), if \(m_c(k) \not = m_r(k)\) or \(m_c'(k) \not = m_r'(k)\),
              \(m_r(k) = m_r'(k)\)
          \end{itemize}
        \item Else, for \(\MP\) and \(M'\) such that \(m_c,p_c \hookrightarrow \MP\) and \(m_c' \hookrightarrow M'\),
          \(\MP \sim_P M'\)
      \end{itemize}
